Advanced Calc Homework 6

### 2017-03-24 311/latex/final.tex
final final

@@

is continuous at $x_0 = 0$. This entails showing that $\forall \epsilon>0$, $\exists \delta>0$ such that $|x-x_0|<\delta$ implies $|f(x)-f(x_0)|<\epsilon$. Consider the following manipulation, where $x_0 = 0$:

@@

\section{Problem 5} \textbf{Prove that if p(x) is a polynomial of degree $n$, then there are most $n$ solutions to the equation $p(x) = 0$.}\\
We will do this by induction. First, we will show the $k=1$ case where $p^{n-1}(x) = 0$ has at most one solution. Then we will show the inductive step $k(i)$ implies $k(i+1)$, that $p^{i}(x) = 0$ has $n$ solutions implies $p^{i-1}(x) = 0$ has at most $n+1$ solutions.\\

\textbf{Base case}\\
Consider degree-n polynomial $p(x)$. Consider the $n-1$th derivative, $p^{n-1}(x)=n\!x+c$. $$p^{n-1}(x)=0$ has at least one solution; consider $x=\frac{-c}{n}$. We want to show this is a unique solution. In search of a contradiction, consider another solution $x_0 \neq \frac{-c}{n}$ such that $p^{n-1}(x_0) = 0$. $p^{n-1}(x)$ is a polynomial, and thus is everywhere differentiable and continuous. Then by Rolle's Theorem $\exists x'$ such that, if $x_0>\frac{-c}{n}$ $x'\in\(\frac{-c}{n},x_0\)$ or if $x_0<\frac{-c}{n}$ $x'\in\(x_0,\frac{-c}{n}\)$ and $p^{n}(x)=0$. However, $p^{n}(x)=n\!$. This is a contradiction. Thus, $p^{n-1}(x)$ has exactly one solution.\\

\textbf{Inductive step}\\

>>>>

\section{Problem 1}
Because $b>1$, by the Archimedean Property, $\exists n \in \mathbb{N}$ such that $b > 1 - \frac{1}{n}$. Now consider:\\

\begin{align*}
  b^n &\geq \left(1 + \frac{1}{n}\right)^n\\
  &= \sum_{i=0}^{n}{n \choose i}\frac{1}{n^i}\\
  &= \sum_{i=2}^{n}{n \choose i}\frac{1}{n^i} + 2
\end{align*}

Thus, since all components of $\sum_{i=2}^{n}{n \choose i}\frac{1}{n^i}$ are positive, $b^n \geq 2$. Thus for any $x>2$, $\exists m \in \mathbb{N}$ such that $m > log_2(x)$ where $b^{n+m} \in \left(b, b^2, b^3, ...\right)$ and $b^{n+m}>x$. Thus, $\left(b, b^2, b^3, ...\right)$ is not bounded from above.\\

@@

is continuous at $x_0 = 0$. This entails showing that $\forall \epsilon>0$, $\exists \delta>0$ such that $|x-x_0|<\delta$ implies $|f(x)-f(x_0)|<\epsilon$. Consider the following manipulation, where $x_0 = 0$. Note that $|f(x)|\leq x$ for all $x$.\\

@@

\section{Problem 4}
Consider the following algebraic manipulation:

\begin{align*}
  \lim_{x\rightarrow0}\frac{f(x)}{g(x)} &= \lim_{x\rightarrow0}\frac{f(x)-f(0)}{g(x)-g(0)}\\
  &= \lim_{x\rightarrow0}\frac{\frac{f(x)-f(0)}{x}}{\frac{g(x)-g(0)}{x}}\\
  &= \frac{f'(0)}{g'(0)}\\
\end{align*}

Note that because $f'$ and $g'$ are continuous at zero, their limits can be taken:

\begin{align*}
  \lim_{x\rightarrow0}\frac{f(x)}{g(x)} &= \lim_{x\rightarrow0}\frac{f'(x)}{g'(x)}\\
\end{align*}

\section{Problem 5} \textbf{Prove that if p(x) is a polynomial of degree $n$, then there are most $n$ solutions to the equation $p(x) = 0$.}\\
We will do this by induction. First, we will show the $k=1$ case where $p^{n-1}(x) = 0$ has at most one solution. Then we will show the inductive step $k(i)$ implies $k(i+1)$, that $p^{i}(x) = 0$ has $j$ solutions implies $p^{i-1}(x) = 0$ has at most $j+1$ solutions.\\

\textbf{Base case}\\
Consider degree-n polynomial $p(x)$. Consider the $n-1$th derivative, $p^{n-1}(x)=n!x+c$. $p^{n-1}(x)=0$ has at least one solution; consider $x=\frac{-c}{n}$. We want to show this is a unique solution. In search of a contradiction, consider another solution $x_0 \neq \frac{-c}{n}$ such that $p^{n-1}(x_0) = 0$. $p^{n-1}(x)$ is a polynomial, and thus is everywhere differentiable and continuous. Then by Rolle's Theorem $\exists x'$ such that, if $x_0>\frac{-c}{n}$ $x'\in(\frac{-c}{n},x_0)$ or if $x_0<\frac{-c}{n}$ $x'\in(x_0,\frac{-c}{n})$ and $p^{n}(x)=0$. However, $p^{n}(x)=n!$. This is a contradiction. Thus, $p^{n-1}(x)$ has exactly one solution.\\

\textbf{Inductive step}\\
We now want to show that if $p^{i}(x)=0$ has $n$ unique solutions, then $p^{i-1}(x)=0$ has at most $n+1$ unique solutions. Let $\{a_1, a_2, a_3, ..., a_n\}$ be the set of unique roots of $p^i(x)=0$. Consider interval $(a_m, a_{m+1})$. Note that, since there are no roots between $a_m$ and $a_{m+1}$, either $\forall x \in (a_m, a_{m+1})$, thus $p^i(x)>0$, or $\forall x \in (a_m, a_{m+1})$, thus $p^i(x)<0$. In the first case, $\lim_{x_0\rightarrow x} \frac{p^{i-1}(x_0)-p^{i-1}(x)}{x_0-x} > 0$, so $x_0>x$ implies $p^{i-1}(x_0)>p^{i-1}(x)$, and $x_0<x$ implies $p^{i-1}(x_0)<p^{i-1}(x)$. Thus if $\exists x' \in (a_m, a_{m+1})$ such that $p^{i-1}(x')=0$, then $\forall x \in (a_m, a_{m+1})$, $x>x'$ implies $p^{i-1}(x)>0$, or if $x<x'$ then $p^{i-1}(x)<0$. In the second case, similarly if $\exists x' \in (a_m, a_{m+1})$ such that $p^{i-1}(x')=0$, then $\forall x \in (a_m, a_{m+1})$, $x>x'$ implies $p^{i-1}(x)<0$, or if $x<x'$ then $p^{i-1}(x)>0$. Thus there can occur only one root in $(a_m,a_{m+1})$.\\

Now consider interval $[a_m,a_{m+1}]$. Note that if either $f(a_m)=0$ or $f(a_{m+1})$, then $\forall x \in (a_m,a_{m+1})$ either $p^{i-1}(x)>0$ or $p^{i-1}(x)<0$ by the strict monotonicity of the closed interval inside the open one. Thus each open interval $[a_m,a_{m+1}]$ has at most one root inside it. There are $n-1$ such open intervals, and thus $n-1$ such roots.\\

Also consider the side intervals $(-\infty,a_1]$ and $[a_n,\infty)$. By a similar reasoning to that above, if any element $x \in (-\infty,a_1]$ or $x \in [a_n,\infty)$ meets criteria $p^{i-1}(x)=0$, then for all other elements $x'\neq x$ in the interval, either $p^{i-1}(x)>0$ or $p^{i-1}(x)<0$. Thus there can be only one root in each of these intervals. Thus, there can be a maximum of $n-1+2=n+1$ roots for $p^{i-1}$.\\

Thus, by induction, $p(x)$ can have at most n roots.\\

\section{Problem Six}
Consider continuous function $f$ and antiderivative $F$ defined as $F(x) = \int_0^{x}f(t)dt$. By the Second Fundamental Theorem of Calculus:\\

\begin{align*}
  f(0) &= F'(0) = \lim_{x_0\rightarrow0} \frac{F(x_0)-F(0)}{x_0}\\
  &= \lim_{x_0\rightarrow0} \frac{\int_0^{x_0}f(t)dt-\int_0^0f(t)dt}{x_0}\\
  &= \lim_{x_0\rightarrow0} \frac{\int_0^{x_0}f(t)dt}{x_0}
\end{align*}

We also know that $f(0) = \lim_{x\rightarrow0}f(0)=c$, thus:

\begin{align*}
  c &= \lim_{x_0\rightarrow0} \frac{\int_0^{x_0}f(t)dt}{x_0}
\end{align*}
